---
title: "Generate data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Generate data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(oscbvar)
```

This vignette goes through how to generate data for the paper: from (atomic) agent predictions, to the full data set including aggregation based methods.

## Generate the agent predictions

Agent predictions are generated using the *gen_atomic_preds* function, which requires two inputs: a list of models for which to generate predictions for (a list of available models can be obtained using the *gen_atomic_list()* function) and a list of settings (the starting point, the minimum estimation size before prediction starts, whether to use a rolling estimation window or not, and which column contains the response variable). The function uses the macrodata set.

```{r, eval = FALSE}
menu <- gen_atomic_list()
list_of_models <- menu[c(2, 6, 9, 10)]
atomic_settings <- list(5, 60, FALSE, 1)
pred_data <- gen_atomic_preds(list_of_models, atomic_settings)
```

This will return a data frame on the format

```{r, include = TRUE, echo = FALSE}
#?builhead(atomdat_2)
```